---
title: 'Report: Data Mining'
author: "Nils, Jan, Rakesh, Benjamin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
```

### Interduction

This report aims to answer the following research question:

Did countries with a higher proportion of billionaires have a higher GDP growth rate in the early 21th century?

```{r}
# load billionaires dataset

billionaires <- here("data_prep", "df_ready.csv") %>%
  read_csv()

# aggregate the number of billionaires by country and assign it to object billionaires_by_country

billionaires_by_country <- billionaires %>%
  group_by(country_of_residence) %>%
  summarise(num_billionaires = n_distinct(full_name))


# Load the gdp dataset
gdp_growth_df <- here("data_prep", "GDP_growth.csv") %>%
  read_csv()

```

## Hypothesis

We hypothesise that countries with a higher proportion of billionaires don't have a higher GDP growth rate in the early 21th century. And if they do, we suspect a causation instead of a causality.

### Methods

We start off by loading the data and then we will aggregate the data to count the number of billionaires by industry.

```{r}

ggplot(billionaires_by_country_gdp, aes(x = reorder(country_of_residence, -num_billionaires), y = num_billionaires)) +
  geom_point(aes(size = gdp_country), color = "blue") +
  labs(x = "Country", y = "Number of Billionaires", title = "Number of Billionaires by Country and GDP") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Results

### Discussion
